Syntax and Semantics of Cedille

### 2018-06-12 docs/semantics/arxiv-version.tex
arxiv version
git-svn-id: https://svn.divms.uiowa.edu/repos/clc/projects/lambda-encodings/implementations/cedille@30780 bd178f5f-7bea-4014-844f-495ca19b8805

\bibliographystyle{plain}

@@

%% Bibliography
\bibliography{biblio}

>>>>

@@

\begin{thebibliography}{10}

\bibitem{constable+86}
Robert~L. Constable, Stuart~F. Allen, Mark Bromley, Rance Cleaveland, J.~F.
  Cremer, R.~W. Harper, Douglas~J. Howe, Todd~B. Knoblock, N.~P. Mendler,
  Prakash Panangaden, James~T. Sasaki, and Scott~F. Smith.
\newblock {\em Implementing mathematics with the Nuprl proof development
  system}.
\newblock Prentice Hall, 1986.

\bibitem{dreyer18}
Derek Dreyer.
\newblock {The Type Soundness Theorem That You Really Want to Prove (and Now
  You Can)}.
\newblock Milner Award Lecture, delivered at Principles of Programming
  Languages (POPL), 2018.

\bibitem{dybjer16}
Peter Dybjer and Erik Palmgren.
\newblock {Intuitionistic Type Theory}.
\newblock In Edward~N. Zalta, editor, {\em The Stanford Encyclopedia of
  Philosophy}. Metaphysics Research Lab, Stanford University, winter 2016
  edition, 2016.

\bibitem{geuvers92}
Herman Geuvers.
\newblock {The Church-Rosser Property for beta-eta-reduction in Typed
  lambda-Calculi}.
\newblock In {\em Proceedings of the Seventh Annual Symposium on Logic in
  Computer Science {(LICS} '92), Santa Cruz, California, USA, June 22-25,
  1992}, pages 453--460. {IEEE} Computer Society, 1992.

\bibitem{kopylov03}
Alexei Kopylov.
\newblock Dependent intersection: {A} new way of defining records in type
  theory.
\newblock In {\em 18th {IEEE} Symposium on Logic in Computer Science {(LICS)}},
  pages 86--95, 2003.

\bibitem{agda}
\mbox{The Agda development team}.
\newblock {\em Agda}, 2018.
\newblock Version 2.5.3.

\bibitem{miquel01}
Alexandre Miquel.
\newblock {The Implicit Calculus of Constructions Extending Pure Type Systems
  with an Intersection Type Binder and Subtyping}.
\newblock In Samson Abramsky, editor, {\em {Typed Lambda Calculi and
  Applications}}, volume 2044 of {\em Lecture Notes in Computer Science}, pages
  344--359. Springer, 2001.

\bibitem{mishraLinger08}
Nathan Mishra{-}Linger and Tim Sheard.
\newblock {Erasure and Polymorphism in Pure Type Systems}.
\newblock In Roberto~M. Amadio, editor, {\em Foundations of Software Science
  and Computational Structures, 11th International Conference, {FOSSACS} 2008,
  Held as Part of the Joint European Conferences on Theory and Practice of
  Software, {ETAPS} 2008, Budapest, Hungary, March 29 - April 6, 2008.
  Proceedings}, volume 4962 of {\em Lecture Notes in Computer Science}, pages
  350--364. Springer, 2008.

\bibitem{peytonjones07}
Simon Peyton~Jones, Dimitrios Vytiniotis, Stephanie Weirich, and Mark Shields.
\newblock {Practical Type Inference for Arbitrary-rank Types}.
\newblock {\em J. Funct. Program.}, 17(1):1--82, January 2007.

\bibitem{pierce+00}
Benjamin~C. Pierce and David~N. Turner.
\newblock Local type inference.
\newblock {\em {ACM} Trans. Program. Lang. Syst.}, 22(1):1--44, 2000.

\bibitem{stump17}
Aaron Stump.
\newblock {The Calculus of Dependent Lambda Eliminations}.
\newblock {\em J. Funct. Program.}, 27:e14, 2017.

\bibitem{stump18}
Aaron Stump.
\newblock {From Realizability to Induction via Dependent Intersection}, 2018.
\newblock in press.

\end{thebibliography}
